---
pagetitle: "{golem} streams"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<link rel="stylesheet" href="//fonts.googleapis.com/css?family=Roboto:300,300italic,700,700italic">
<link rel="stylesheet" href="//cdnjs.cloudflare.com/ajax/libs/normalize/5.0.0/normalize.css">
<link rel="stylesheet" href="//cdnjs.cloudflare.com/ajax/libs/milligram/1.3.0/milligram.css">
<link rel="stylesheet" href="style.css">

<link href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/4.2.0/css/font-awesome.min.css" rel="stylesheet">


## Watch the `{golem}` team code live!

Join us on Twitch for live-coding sessions! During these streams, we will be building Shiny apps live using the `{golem}` package.

<div align = "center">

#### `r emo::ji("link")` https://www.twitch.tv/thinkr_fr `r emo::ji("link")`

</div>

<!--<div id="twitch-embed"></div>

<script src="https://embed.twitch.tv/embed/v1.js"></script>

<script type="text/javascript">
  var embed = new Twitch.Embed("twitch-embed", {
    width: 854,
    height: 480,
    channel: "thinkr_fr",
    layout: "video",
    autoplay: false
  });

  embed.addEventListener(Twitch.Embed.VIDEO_READY, () => {
    var player = embed.getPlayer();
    player.play();
  });
</script>-->

## Upcoming Stream(s)

### 2nd live stream

<li> `r emo::ji("man_technologist")` Colin Fay, <a href = "https://twitter.com/_ColinFay">@_ColinFay</a> </li>

<li> `r emo::ji("link")` https://www.twitch.tv/thinkr_fr </li>

<li> `r emo::ji("time")` __2020-01-23 21.00 Paris Time__. </li>

```{r echo = FALSE, message=FALSE}
library(magrittr)
library(lubridate)
d <- ymd_hm("2020-01-23 21.00", tz = "Europe/Paris")
list(
  "UTC" = with_tz(d, "UTC"),
  "America/New_York" = with_tz(d, "America/New_York"),
  "America/Los_Angeles" = with_tz(d, "America/Los_Angeles"),
  "Australia/Sydney" = with_tz(d, "Australia/Sydney")
) %>%
  details::details(summary = 'See Event in Other Timezones')
```

## Past Stream(s)

### First live stream `r emo::ji("birthday_cake")` 

<li> `r emo::ji("man_technologist")` Colin Fay, <a href = "https://twitter.com/_ColinFay">@_ColinFay</a> </li>

<li> `r emo::ji("link")` https://www.twitch.tv/thinkr_fr </li>

<li> `r emo::ji("time")` __2020-01-13 21.00 Paris Time__. </li>

## `{golem}`

`{golem}` is a framework for building production grade Shiny Apps. 

Learn more about `{golem}` at: https://github.com/ThinkR-open/golem

<hr>

<div align = "center" class="nav-footer">
  <h4>ThinkR is a french compagny of R experts.</h4>
  <p>Find us on the web:</p>
  <ul>
    <li><a href="https://rtask.thinkr.fr"> <i class="fa fa-link fa-3x"></i> </a></li>
    <li><a href="https://twitter.com/thinkr_fr"> <i class="fa fa-twitter fa-3x"></i> </a></li>
    <li><a href="https://github.com/thinkr-open"> <i class="fa fa-github fa-3x"></i> </a> </li>  
    <li><a href="contact@thinkr.fr"> <i class="fa fa-envelope fa-3x"></i> </a></li>
    </ul>
</div>

<hr>

<div>
Website built on top of [milligram.css](https://milligram.io/).
</div>

